{\LARGE \textsc{Structural controlability of pollination networks}}

### 2016-03-10 paper/manuscript.Rnw
add some more results

We assumed that for a pair of interacting species the direction of control is inverse to the direction of dependency. If, for instance, a plant species depends more on a pollinator species than the pollinator depends on the plant, we expect the plant abbundances to be more sensitive to changes in the pollinator abbundance than vice versa. Violation of this assumption, however, renders qualitatively consistent results (Figure S1; Table S2). Therefore, we first assigned a single direction to each link between plants and pollinators based on the direction the assymetries in dependencies based on visitation frequencies following \textcite{Bascompte2006}. The dependency of plant $i$ on pollinator $j$ is the proportion of the visits comming from pollinator $j$ compared to all pollinator visits to plant $i$. Likewise, the dependency of pollinator $j$ on plant $i$ is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.

@@

\subsection*{Visitation as proxy for species interdependence}

@@

wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)

m0 <- glm(cbind(n_dr, n_sp) ~ n_pla * n_pol, 
          data = n_driver, 
          family = "binomial")
m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
          data = n_driver, 
          family = "binomial")
m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol), 
          data = n_driver, 
          family = "binomial")
m2 <- glm(cbind(n_dr, n_matched) ~ study, 
          data = n_driver, 
          family = "binomial")
@

We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(mean(n_driver$n_dr_p)*100)}\%) of the species in the community. The relative number of driver species did not change if the dependencies were assumed to be bidirectional, or exclusively from plant to pollinators or from pollinators to plants (Figure S1; Table S2). In addition we did not detect any significant differences between the proportion of driver species in invaded or uninvaded ecosystems (Wilcoxon signed-rank sum test, $p = \Sexpr{round(wt$p.value, digits = 3)}$) nor between study sites (likelyhood ratio test, $Pr(>\chi^2) = \Sexpr{round(anova(m1, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; Table S3). Nevertheless we found that the ratio of plant to pollinator species richness had an important neggative effect on the proportion of driver species ($Pr(>\chi^2) = \Sexpr{round(anova(m2, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$; \autoref{fig:n_driver_explanatory}, Table S3).

@@

We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks. We found that empirical networks have a much larger  the importance of dependency

\begin{figure}
\centering
<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=
r <- r_w %>%
  dplyr::bind_rows(r_d) %>%
  dplyr::inner_join(meta) %>%
  dplyr::filter(count == "visitation") %>%
  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)

@@

@@

z_scores %>%
  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
                m_n = as.numeric(method),
                m_n = replace(m_n, m_n == 3, 3.5)) %>%
  ggplot(aes(x = m_n, y = z_s)) +
  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
  geom_vline(xintercept = c(2.75), alpha = 0.7, size = 0.25) +
  geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
  geom_boxplot(aes(group = method), size = 0.25, colour = "grey10",
							 outlier.shape = 21, outlier.size = 1) +
  geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
  coord_flip() +
  scale_colour_manual(values = c(NA, "black")) +
  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("dependency", "strength", "degree"))) + 
  xlab("") +
  ylab("number of driver species (z-score)") + 
  fer_theme +
  theme(axis.text.x = element_text(angle = 90), 
        legend.position = "none",
				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
				# panel.grid.minor.x = element_blank(),
				panel.grid.minor.y = element_blank())

@@

@@

The authors thank Dr. Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon and Marilia Gaiarsa for feedback in early stages of the project. EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS). DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.

>>>>

We assumed that for a pair of interacting species the direction of control is inverse to the direction of dependency. If, for instance, a plant species depends more on a pollinator species than the pollinator depends on the plant, we expect the plant abbundances to be more sensitive to changes in the pollinator abbundance than vice versa. However, our results are robust to this assumption as its violation renders qualitatively consistent results (Figure S1 and S2; Table S2). Therefore, we first assigned a single direction to each link between plants and pollinators based on the direction the assymetries in dependencies based on visitation frequencies following \textcite{Bascompte2006}. The dependency of plant $i$ on pollinator $j$ is the proportion of the visits comming from pollinator $j$ compared to all pollinator visits to plant $i$. Likewise, the dependency of pollinator $j$ on plant $i$ is the ratio of the visits by pollinator $j$ to plant $i$ and all visits of pollinator $j$.

@@

\subsection*{Visitation as a proxy for species interdependence}

@@

wt <-  wilcox.test(x = wt[, 1], y = wt[, 2], paired = T)
m0 <- glm(cbind(n_dr, n_matched) ~ n_pla * n_pol + study + inv, 
          data = n_driver, 
          family = "binomial")
m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study + inv, 
          data = n_driver, 
          family = "binomial")
m8 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + inv, 
          data = n_driver, 
          family = "binomial")
m9 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
          data = n_driver, 
          family = "binomial")
m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol), 
          data = n_driver, 
          family = "binomial")
m2 <- glm(cbind(n_dr, n_matched) ~ study, 
          data = n_driver, 
          family = "binomial")
m3 <- glm(cbind(n_dr, n_matched) ~ I(n_pla + n_pol), 
          data = n_driver, 
          family = "binomial")
m4 <- glm(cbind(n_dr, n_matched) ~ n_pla, 
          data = n_driver, 
          family = "binomial")
m5 <- glm(cbind(n_dr, n_matched) ~ n_pol, 
          data = n_driver, 
          family = "binomial")
m6 <- glm(cbind(n_dr, n_matched) ~ inv, 
          data = n_driver, 
          family = "binomial")
m7 <- glm(cbind(n_dr, n_matched) ~ study + inv, 
          data = n_driver, 
          family = "binomial")
@

We found that if we were to control the dynamics of the whole community, we would need to control between \Sexpr{round(min(n_driver$n_dr_p)*100)} and \Sexpr{round(max(n_driver$n_dr_p)*100)}\% (mean \Sexpr{round(mean(n_driver$n_dr_p)*100)}\%) of the species in the community---which corresponds to manageabilities of \Sexpr{round(min(1-n_driver$n_dr_p), digits = 2)} to \Sexpr{round(max(1-n_driver$n_dr_p), digits = 2)} (Table S1). In addition we found that the ratio of plant to pollinator species richness had an important possitive effect on the community manageability ($Pr(>\chi^2) = \Sexpr{round(anova(m2, m_nr, test = "LRT")$`Pr(>Chi)`[2], digits = 3)}$). Constrastingly measures of biodiversity (like plant or pollinator richness) or factors such as the status of invasion, or the location of the study did not have a significant effect on the manageability (\autoref{fig:n_driver_explanatory}, Table S3).

@@

<<randomisations z_scores, echo = FALSE, warning= FALSE, message = FALSE>>=
r <- r_w %>%
  dplyr::bind_rows(r_d) %>%
  dplyr::inner_join(meta) %>%
  dplyr::filter(count == "visitation") %>%
  dplyr::mutate(n_dr = n_pla + n_pol - n_matched)

@@

@

We found that the manageability of empirical networks is not significantly different to that of network randomisations that maintained the species strength but different to those that maintained species degree (two tailed t-test, $p = \Sexpr{round(unique(dplyr::filter(z_scores, method == "quasiswap_count")$sign), digits = 3)}$ and \Sexpr{round(unique(dplyr::filter(z_scores, method == "swsh_both")$sign), digits = 3)} respectively; \autoref{fig:randomisations}). This result was also robust to the assumption that bidirectional shit (FIgure Sx)\todo{finish those analysis}.

found that species strength and not degree structures the manageability of empirical networks (). 
We examined the role that the asimmetry of the dependencies which defines the direction of control has a central role in structuring the controlability of polination networks. We found that empirical networks have a much larger  the importance of dependency

\begin{figure}
\centering
<<fig randomisations, echo = FALSE, warning = F, message = F, fig.height=2.2, fig.width=3.1>>=

@@

z_scores %>%
  dplyr::mutate(method = factor(method, levels = z_scores_method_order),
                m_n = as.numeric(method),
                m_n = replace(m_n, m_n == 3, 3.5)) %>%
  ggplot(aes(x = m_n, y = -1 * z_s)) +
  # geom_hline(yintercept = c(-0), linetype = 2, alpha = 0.7, size = 0.25) + 
  geom_vline(xintercept = c(2.75), alpha = 0.6, size = 0.25) +
  geom_hline(yintercept = 0, size = 0.25, linetype = 2, colour = "grey30") +
  geom_boxplot(aes(group = method, fill = sign <= 0.05), size = 0.25, colour = "grey10",
							 outlier.shape = 21, outlier.size = 1) +
  # geom_point(aes(y = 9, colour = sign <= 0.05), shape = 8, size = 1) +
  coord_flip() +
  scale_fill_manual(values = c("white", "#bdbdbd")) +
  scale_x_continuous(breaks = c(1, 2, 3.5), labels = rev(c("random\ndependency", "maintain strength\nrandomise degree", "maintain degree\nrandomise strength"))) + 
  xlab("") +
  ylab("Z-score of emp. manageability") + 
  fer_theme +
  theme(axis.text.x = element_text(angle = 90), 
        legend.position = "none",
				plot.margin = grid::unit(c(2, 1, 2, 0), "mm"), 
				# panel.grid.minor.x = element_blank(),
				panel.grid.minor.y = element_blank())

@@

<<eval = F, echo = F>>=
z_scores %>%
  dplyr::filter(method == "r0") %>%
  dplyr::inner_join(n_driver) %>%
  ggplot(aes(x = n_pla/n_pol, y = z_s)) +
  geom_point()

r %>%
  dplyr::filter(method == "r0")  %>%
  dplyr::inner_join(n_driver, by = "net_name") %>%
  ggplot(aes(x = n_pla.y/n_pol.y, y = n_matched.x / (n_pla.y + n_pol.y))) +
  geom_point() +
  geom_smooth(method = "glm")
@

@@

The authors thank Dr. Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Bernat Bramon, Matthew Hutchinson and Marilia Gaiarsa for feedback in early stages of the project. EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushroooms Postgraduate Scholarship, a travel grant from the European Space Agency and a Rutherford Discovery Fellowship (to DBS). DBS ackloledges the support of a Rutherford Discovery Scholarship, administered by the Royal Society of New Zealand.
